---
title: "ACES_CRS_OCD"
output: html_document
date: "2023-04-05"
---
# Interactive effect of ACEs and CRS on OCD symptom severity

```{r}
getwd()
library(readr)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(stringr)
library(haven)
library(summarytools)
library(interactions)
library(ggpubr)
```
This chunk calls the packages needed for figures

## Importing, cleaning, and making new dataset
### Import
```{r}
#Set your file destination
setwd("~/Desktop/Coding/R working directory/datafiles")
#Set where your dataset is, you can use the import button and copy that here.
ADAA_dup <- read_sav("/Users/troyhubert/Desktop/Coding/R working directory/datafiles/ADAA_SubmissionDataset.sav")
```

### Clean
```{r}
# Make new DF with no duplicates______________
ADAA_no_dup <- ADAA_dup %>%
  filter(Missing_or_Dup==0)
# Check for missing or duplicates
sum(ADAA_no_dup$Duplicate)
sum(ADAA_no_dup$Missing_Data)
# Code Variables for analysis_________________

#ACE as integer 
ADAA_no_dup$ace_tot = as.integer(ADAA_no_dup$ace_tot)

#Change White 
str(ADAA_no_dup$White)

ADAA_no_dup$White <-as.factor(ADAA_no_dup$White)
levels(ADAA_no_dup$White) <- Race_level<-c("Not White", "White")

#Change Gender 
ADAA_no_dup$sex <- as.factor(ADAA_no_dup$sex)
levels(ADAA_no_dup$sex) <- Sex_level<-c("Male","Female")

#Change Ethn 
ADAA_no_dup$ethn <- as.factor(ADAA_no_dup$ethn)

#change ACEs for Plot
ADAA_no_dup$ACEs <- ADAA_no_dup$ace_tot
```

## Select variables for new DF
```{r}
Em_ADAA <- ADAA_no_dup%>%
  filter(IncludeCases == 1) %>%
  select(record_id,IncludeCases,White,sex,ethn, ACEs, crs_tot,DOCStot,DOCSCon,DOCSResp,DOCSUnTh,DOCSSym)
Em_ADAA
str(Em_ADAA)
```
# Figures

## Figure 1 - Interaction total OCD severity
```{r}

#Define model
DOCS_mod = glm(DOCStot~crs_tot*factor(ACEs)+White+ethn+sex, data=Em_ADAA)

#create Interaction Plot 
DOCS_IntPlot = interact_plot(DOCS_mod, pred = crs_tot, modx = ACEs, 
                             modx.values = c(0, 1, 4), 
                             interval = TRUE, int.width = 0.8,
                             centered="all", colors = c("#00BFC4","#368bd1","#0263a3"))
DOCS_IntPlot$labels$x = "Covid Related Stress"
DOCS_IntPlot$labels$y = "Total DOCS Score"
DOCS_IntPlot$theme= theme_classic()
DOCS_IntPlot
```

## Figure 2 - JN PLOT - Total OCD Severity

```{r}
#define model
  #This was already done above, but for referene
DOCS_mod = glm(DOCStot~crs_tot*factor(ACEs)+White+ethn+sex, data=Em_ADAA)

#create jn plot
DOCS_jnplot = sim_slopes(DOCS_mod, pred = crs_tot, modx = ACEs, 
                         jnplot = TRUE, 
                         centered="all", 
                         mod.range=c(0,10), 
                         sig.color = "#F8766D",
                        insig.color = "#00BFC4",
                         title=" ")#Johnson neyman plot

#Edit plot
DOCS_plot = DOCS_jnplot$jnplot
DOCS_plot$labels$y = "B (95% CI) of CRS on DOCS"
DOCS_plot$labels$title=NULL
DOCS_plot$labels$x = "ACES"
DOCS_plot$labels$fill=NULL
DOCS_plot$theme= theme_classic()
DOCS_plot$labels$fill=NULL
DOCS_plot<-DOCS_plot+ scale_x_discrete(limits=c(0,1,2,3,4,5,6,7,8,9,10))
DOCS_plot
```
Putting them together
```{r}
ggarrange(DOCS_IntPlot, DOCS_plot, ncol = 2, nrow = 1)
```

### Figure 3 OCD Dimensions
```{r}
# CONTAMINATION _________________________________
#define model
Con_mod = glm(DOCSCon~crs_tot*factor(ACEs)+White+ethn+sex, data=Em_ADAA)
#create Interaction Plot 
DOCS_ConInt = interact_plot(Con_mod, pred = crs_tot, modx = ACEs, 
                             modx.values = c(0, 1, 4), 
                             interval = TRUE, int.width = 0.8,
                             centered="all",
                            colors = c("#00BFC4","#368bd1","#0263a3"))
DOCS_ConInt$labels$x = "Covid Related Stress"
DOCS_ConInt$labels$y = "Contamination Score"
DOCS_ConInt$theme= theme_classic()
DOCS_ConInt

#RESPONSIBILITY _____________________________
#define model
Resp_mod = glm(DOCSResp~crs_tot*factor(ACEs)+White+ethn+sex, data=Em_ADAA)
#create Interaction Plot 
DOCS_RespInt = interact_plot(Resp_mod, pred = crs_tot, modx = ACEs, 
                             modx.values = c(0, 1, 4), 
                             interval = TRUE, int.width = 0.8,
                             centered="all",
                            colors = c("#00BFC4","#368bd1","#0263a3"))
DOCS_RespInt$labels$x = "Covid Related Stress"
DOCS_RespInt$labels$y = "Responsibility Score"
DOCS_RespInt$theme= theme_classic()
DOCS_RespInt

#UNACCEPTABLE THOUGHTS  _____________________________
#define model
UnTh_mod = glm(DOCSUnTh~crs_tot*factor(ACEs)+White+ethn+sex, data=Em_ADAA)
#create jn plot
DOCS_UnThInt = interact_plot(UnTh_mod, pred = crs_tot, modx = ACEs, 
                             modx.values = c(0, 1, 4), 
                             interval = TRUE, int.width = 0.8,
                             centered="all",
                             colors = c("#00BFC4","#368bd1","#0263a3"))
DOCS_UnThInt$labels$x = "Covid Related Stress"
DOCS_UnThInt$labels$y = "Unacceptable Thoughts Score"
DOCS_UnThInt$theme= theme_classic()
DOCS_UnThInt

#SYMMETRY  _____________________________
#define model
Sym_mod = glm(DOCSSym~crs_tot*factor(ACEs)+White+ethn+sex, data=Em_ADAA)
#create jn plot
DOCS_SymInt = interact_plot(Sym_mod, pred = crs_tot, modx = ACEs, 
                             modx.values = c(0, 1, 4), 
                             interval = TRUE, int.width = 0.8,
                             centered="all",
                             colors = c("#00BFC4","#368bd1","#0263a3"))
DOCS_SymInt$labels$x = "Covid Related Stress"
DOCS_SymInt$labels$y = "Symmetry Score"
DOCS_SymInt$theme= theme_classic()
DOCS_SymInt
```

Figure 4 - OCD dimentions JN plot
```{r}
# CONTAMINATION _________________________________
#define model
Con_mod = glm(DOCSCon~crs_tot*factor(ACEs)+White+ethn+sex, data=Em_ADAA)
#create jn plot
Con_jnplot = sim_slopes(Con_mod, pred = crs_tot, modx = ACEs, 
                        jnplot = TRUE, 
                        centered="all", 
                        mod.range=c(0,10), 
                        sig.color = "#F8766D",
                        insig.color = "#00BFC4",
                        title=" ")#Johnson neyman plot
#Edit plot
Con_plot = Con_jnplot$jnplot
Con_plot$labels$y = "Contamination (B 95% CI)"
Con_plot$labels$title=NULL
Con_plot$labels$x = "ACES"
Con_plot$labels$fill=NULL
Con_plot$theme= theme_classic()
Con_plot$labels$fill=NULL
Con_plot<-Con_plot+ scale_x_discrete(limits=c(0,1,2,3,4,5,6,7,8,9,10))
Con_plot

#RESPONSIBILITY _____________________________
#define model
Resp_mod = glm(DOCSResp~crs_tot*factor(ACEs)+White+ethn+sex, data=Em_ADAA)
#create jn plot
Resp_jnplot = sim_slopes(Resp_mod, pred = crs_tot, modx = ACEs, 
                         jnplot = TRUE, 
                         centered="all", 
                         mod.range=c(0,10), 
                         sig.color = "#F8766D",
                        insig.color = "#00BFC4",
                         title=" ")
#Edit plot
Resp_plot = Con_jnplot$jnplot
Resp_plot$labels$y = "Responsibility (B 95% CI)"
Resp_plot$labels$title=NULL
Resp_plot$labels$x = "ACES"
Resp_plot$labels$fill=NULL
Resp_plot$theme= theme_classic()
Resp_plot$labels$fill=NULL
Resp_plot<-Resp_plot+ scale_x_discrete(limits=c(0,1,2,3,4,5,6,7,8,9,10))
Resp_plot

#UNACCEPTABLE THOUGHTS  _____________________________
#define model
UnTh_mod = glm(DOCSUnTh~crs_tot*factor(ACEs)+White+ethn+sex, data=Em_ADAA)
#create jn plot
UnTh_jnplot = sim_slopes(UnTh_mod, pred = crs_tot, modx = ACEs, 
                         jnplot = TRUE, 
                         centered="all", 
                         mod.range=c(0,10), 
                         sig.color = "#F8766D",
                        insig.color = "#00BFC4",
                         title=" ")#Johnson neyman plot
#Edit plot
UnTh_plot = UnTh_jnplot$jnplot
UnTh_plot$labels$y = "Unacceptable Thoughts (B 95% CI)"
UnTh_plot$labels$title=NULL
UnTh_plot$labels$x = "ACES"
UnTh_plot$labels$fill=NULL
UnTh_plot$theme= theme_classic()
UnTh_plot$labels$fill=NULL
UnTh_plot<-UnTh_plot+ scale_x_discrete(limits=c(0,1,2,3,4,5,6,7,8,9,10))
UnTh_plot

#SYMMETRY  _____________________________
#define model
Sym_mod = glm(DOCSSym~crs_tot*ACEs+White+ethn+sex, data=Em_ADAA)
#create jn plot
Sym_jnplot = sim_slopes(Sym_mod, pred = crs_tot, modx = ACEs, 
                        jnplot = TRUE, 
                        centered="all", 
                        mod.range=c(0,10), 
                        sig.color = "#F8766D",
                        insig.color = "#00BFC4",
                        title=" ")#Johnson neyman plot
#Edit plot
Sym_plot = UnTh_jnplot$jnplot
Sym_plot$labels$y = "Symmetry (B 95% CI)"
Sym_plot$labels$title=NULL
Sym_plot$labels$x = "ACES"
Sym_plot$labels$fill=NULL
Sym_plot$theme= theme_classic()
Sym_plot$labels$fill=NULL
Sym_plot<-Sym_plot+ scale_x_discrete(limits=c(0,1,2,3,4,5,6,7,8,9,10))
Sym_plot
```

```{r}
# PUTTING THEM ALL TOGETHER_______________
ggarrange(Con_plot, Resp_plot, UnTh_plot, Sym_plot,
          ncol = 2, nrow = 2)
```

Putting the groups together

```{r}
ggarrange(DOCS_ConInt, Con_plot, ncol = 2, nrow = 1)

ggarrange(DOCS_RespInt, Resp_plot, ncol = 2, nrow = 1)

ggarrange(DOCS_UnThInt, UnTh_plot, ncol = 2, nrow = 1)

ggarrange(DOCS_SymInt, Sym_plot, ncol = 2, nrow = 1)
```


